Quantifying Lewontin's Paradox Suggests Natural Selection is Unlikely to Explain the Narrow Range of Diversity Among Species

### 2021-06-04 manuscript/elife/elife-template.tex
more formatting crap

\figdata{The complete diversity and population size dataset for 172 metazoan taxa.}

@@

   \figsupp{Pairwise diversity grouped by the range categories from
    \cite{Leffler2012-zj}, with point size indicating the predicted population
    density. The vertical lines are the range category group
  means.}{\includegraphics{figures/diversity_leffler_ranges.pdf}}\label{figsupp:div-leffler}
  \end{fullwidth}
\end{figure}

@@

>>>>

\figdata{The population size estimates for 172 metazoan taxa.}

@@

   \figsupp{Pairwise diversity grouped by the range categories from
    \cite{Leffler2012-zj}, with point size indicating the predicted population
    density. The vertical lines are the range category group
  means.}{\includegraphics{figures/diversity_leffler_ranges.pdf}}\label{figsupp:div-leffler}
  \end{fullwidth}
\figdata{The diversity and population size dataset for 172 metazoan taxa.}
\end{figure}

@@

  \end{fullwidth}
\figdata{The map length, population size, and linked selection estimates for 136 metazoan taxa.}
\end{figure}
